### 2014-09-25 fundamentals/examples.tex
citation

The archetypes created by user-developers 
and the archetypes provided in the \Cycamore repository of additional modules 
together form an `ecosystem' of capabilities. Since the long term vision for 
the \Cyclus framework includes an ever-expanding ecosystem of both general and 
specialized capability extensions within that ecosytem. The early growth and 
cross-institutional contributions to this ecosystem demonstrates a significant 
acheivement by the \Cyclus framework.

>>>>

The archetypes created by user-developers and the archetypes provided in the 
\Cycamore \cite{carlsen_cycamore_2014} repository of additional modules 
together form an `ecosystem' of capabilities. Since the long term vision for 
the \Cyclus framework includes an ever-expanding ecosystem of both general and 
specialized capability extensions within that ecosytem. The early growth and 
cross-institutional contributions to this ecosystem demonstrates a significant 
acheivement by the \Cyclus framework.
